%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventrytwopositions
  {Software Engineer II - Storage Spaces Dev Team} % Job title 1
  {Microsoft Corporation} % Organization
  {Redmond, WA, USA} % Location
  {Sep. 2015 - Jan. 2022} % Date(s) for Job title 1
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
        Optimized Storage Spaces Repair (i.e., RAID resilvering) by enhancing Storage
        Spaces metadata to track stale logical data copies at stripe granularity
        (i.e., 256 KiB) vs. extent granularity (i.e., 256 MiB) previously, which
        reduced the run time of Storage Spaces Repair from hours to minutes.
      }
      \item {
        Implemented Storage Spaces support for configuring, deploying, and managing
        Storage Spaces with node-mirrored mirror and node-mirrored parity multilevel
        resiliency settings on 2-node Storage Spaces Direct (S2D) Failover Clusters,
        which enables Storage Spaces on 2-node S2D Failover Clusters to tolerate 1
        node + 1 drive failures vs. 1 node failure previously.
      }
      \item {
        Designed and implemented an extra-resilient cache for staging writes to
        Storage Space ranges backed by a suboptimal number of logical copies to
        enable write forward progress without compromising on redundancy and risking
        data loss.
      }
    \end{cvitems}
  }
  {Senior Software Engineer - Hyper-V Virtualization Infrastructure Services Team} % Job title 2
  {Jan. 2022 - Present} % Date(s) for Job title 2
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
        Implemented Hyper-V virtualization stack support for Virtualization
        Infrastructure Driver (VID.sys) runtime reload during an Ultralite Virtual
        Machine Preserving Host Update (VM-PHU) with Handle Brokering, which enables
        VID.sys to be runtime reloaded during a VM-PHU without requiring a host
        reboot or storage/network I/O drain, which are known bottlenecks.
      }
      \item {
        Contributed to the design and implementation of Virtual Processor (VP) Auto
        Suspend for VM-PHU, which defers VP suspend to the Windows Hypervisor until
        the arrival of root partition intercepts, thereby minimizing VM compute
        blackout during VM-PHU and enabling Hyper-V virtualization stack components
        to be serviced on the host while VMs are still running.
      }
    \end{cvitems}
  }

  \cventry
    {Compiler Optimization Developer (Intern)} % Job title
    {IBM Canada Ltd.} % Organization
    {Markham, ON, Canada} % Location
    {Sep. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Assisted with the implementation of a translator for translating LLVM IR to
          the intermediate representation used by IBM's XL C/C++/Fortran compiler.
        }
        \item {
          Expanded test coverage for IBM's LLVM IR translator by writing a program in
          C/C++ to spoof IBM's XL C/C++/Fortran compiler test drivers so that its test
          buckets could be reused for validating IBM's LLVM IR translator.
        }
      \end{cvitems}
    }

  \cventry
    {Operations Technology Developer (Intern)} % Job title
    {Citigroup Inc.} % Organization
    {Mississauga, ON, Canada} % Location
    {Sep. 2013 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Automated a bookkeeping workflow at Citigroup by writing a program in Java to
          periodically scrape financial data from an internal website using Selenium
          and format the data to Excel, which saved a bookkeeper over an hour per day
          otherwise spent doing manual data entry.
        }
        \item {
          Implemented automated tests for Citigroup's Global Stock Record
          (GSR) web frontend using Java and Selenium to reduce reliance on manual
          testing.
        }
      \end{cvitems}
    }

  \cventry
    {System Software Developer (Intern)} % Job title
    {Nav Canada} % Organization
    {Ottawa, ON, Canada} % Location
    {Apr. 2012 - Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Ported Nav Canada's air traffic control software build distribution tool from
          HP-UX to Red Hat Enterprise Linux with a Java ICEFaces web frontend, which
          simplified the air traffic control software build distribution workflow by
          automating steps that were previously performed manually.
        }
      \end{cvitems}
    }

\end{cventries}
