%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Internships}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Compiler Optimization Developer} % Job title
    {IBM Canada Ltd.} % Organization
    {Markham, ON, Canada} % Location
    {Sep. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Assisted with implementing an instruction translator for translating LLVM IR to an
          intermediate representation used by IBM's XL C/C++ compilers.
        }
        \item {
          Expanded the test coverage for IBM's LLVM IR translator by implementing a program in C++
          to impersonate IBM's XL C/C++ compiler test drivers so that existing test buckets for
          IBM's XL C/C++ compilers could be reused for validating IBM's LLVM IR translator.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Operations Technology Developer} % Job title
    {Citigroup Inc.} % Organization
    {Mississauga, ON, Canada} % Location
    {Sep. 2013 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Automated an hourly bookkeeping workflow at Citigroup by implementing a small program in
          Java to scrape financial data from a website using Selenium and format the data to Excel
          spreadsheets, and deploying this program hourly using Jenkins. This effort ended up
          saving a bookkeeper over an hour a day otherwise spent entering the data by hand.
        }
        \item {
          Reduced time cost of validating Citigroup's Global Stock Record (GSR) web app by
          automating black-box testing using Java and Selenium.
        }
        \item {
          Provided consultation to other developers to scale GSR's automated black-box test
          framework for validating other Citigroup web apps.
        }
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
{System Software Developer} % Job title
{Nav Canada} % Organization
{Ottawa, ON, Canada} % Location
{Apr. 2012 - Aug. 2012} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {
      Assisted with porting an air traffic control software build distribution tool from HP-UX to
      a Java ICEFaces web app hosted on a Red Hat Linux server.
    }
    \item {
      Reduced the learning curve and improved quality of life around using the new air traffic
      control software build distribution tool by automating steps in the build distribution
      workflow that previously had to be executed manually using the old tool.
    }
  \end{cvitems}
}

%---------------------------------------------------------

\end{cventries}
